Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-03-07 docs/00-manuscripts/ieee/ieee-manuscript.tex
merge local changes

Airborne hyperspectral data with a spatial resolution of one meter and 126 spectral bands was available for four Monterey Pine (\textit{Pinus radiata D. Don}) plantations in northern Spain.
The trees in the plots suffer from infections of invasive pathogens such as \textit{Diplodia sapinea (Fr.) Fuckel}, \textit{Fusarium circinatum Nirenberg \& O'Donnell}, \textit{Armillaria mellea (Vahl) P. Kumm}, \textit{Heterobasidion annosum (Fr.) Bref}, \textit{Lecanosticta acicola (Thüm) Syd.} and \textit{Dothisthroma septosporum (Dorogin) M. Morelet} causing a spread of cankers or defoliation \cite{mesanza2016, iturritxa2017}.
The last two fungi are mainly responsible for the foliation loss of the trees analyzed in this study \cite{iturritxa2014}.
In-situ measurements of defoliation of trees (serving as a proxy for tree health) were collected to serve as the response variable \textit{defoliation} which ranges from 0 - 100 (in \%) (\autoref{fig:defol-distr}).
It is assumed that the fungi infect the trees through open wounds, possibly caused by previous hail damage \cite{iturritxa2014}.
The dieback of these trees, which are mainly used as timber, causes high economic damages \cite{ganley2009}.

@@

The airborne hyperspectral data was acquired during two flight campaigns which took place at noon on September 28th and October 5th 2016.
The images were taken by an AISAEAGLE-II sensor.
All preprocessing steps (geometric, radiometric, atmospheric) were conducted by the \ac{ICGC}.
The first four bands were corrupted, leaving 122 bands with valid information.
Additional metadata information is available in \autoref{tab:hyperparameter_metadata}.

@@

\begin{quote}
The image acquisitions were originally attempted during one day (29) but due to the variable meteorological conditions some stands had to be imaged the next day.
\end{quote}

>>>>

Airborne hyperspectral data with a spatial resolution of one meter and 126 spectral bands was available for four Monterey Pine (\textit{Pinus radiata D. Don}) plantations in northern Spain.
The trees in the plots suffer from infections of invasive pathogens such as \textit{Diplodia sapinea (Fr.) Fuckel}, \textit{Fusarium circinatum Nirenberg \& O'Donnell}, \textit{Armillaria mellea (Vahl) P. Kumm}, \textit{Heterobasidion annosum (Fr.) Bref}, \textit{Lecanosticta acicola (Thüm) Syd.} and \textit{Dothisthroma septosporum (Dorogin) M. Morelet} causing a spread of cankers or defoliation \cite{mesanza2016, iturritxa2017}.
The last two fungi are mainly responsible for the foliation loss of the trees analyzed in this study \cite{iturritxa2014}.
In-situ measurements of defoliation of trees (serving as a proxy for tree health) were collected to serve as the response variable \textit{defoliation} which ranges from 0 - 100 (in \%) (\autoref{fig:defol-distr}).

It is assumed that the fungi infect the trees through open wounds, possibly caused by previous hail damage \cite{iturritxa2014}.
The dieback of these trees, which are mainly used as timber, causes high economic damages \cite{ganley2009}.

@@

The airborne hyperspectral data was acquired during two flight campaigns which took place at noon on September 28th and October 5th 2016.
The images were taken by an AISA EAGLE-II sensor.
All preprocessing steps (geometric, radiometric, atmospheric) were conducted by the \ac{ICGC}.
The first four bands were corrupted, leaving 122 bands with valid information.
Additional metadata information is available in \autoref{tab:hyperparameter_metadata}.

@@

\begin{quote}
The image acquisitions were originally attempted during one day (29.10.2016) but due to the variable meteorological conditions some stands had to be imaged the next day.
\end{quote}
